Weather Data Integration and Assimilation System\\

### 2020-02-14 method/sec_3-microservice.tex
change API with texttt

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\acrshort{wdias} Microservices}
\label{sebse:wdias_microservices}
As seen in Figure of \cref{fi:wdias_micro_on_demand} and \cref{fi:wdias_micro_async} each circle represents a microservice, and those are implemented as containerized applications.
\begin{figure}[htp]
    \centering
    \includegraphics[width=1\textwidth]{method/microservice/microservice_architecture-handle_on_demand-v3.jpg}
    \caption{\acrshort{wdias} architecture for handling requests on demand}
    \label{fi:wdias_micro_on_demand}
\end{figure}
Left side of \cref{fi:wdias_micro_on_demand} shows the import modules of the \acrshort{wdias}, and right side shows the export modules. As it explained section \cref{subse:dumb_pipes}, each import microservice only do specific task of converting and forwarding the request to the correct data adapter module.
For each data type, there is a adapter microservice is running which is optimized to storing such type of data. And the metadata data of the timeseries store using \acrshort{rdbms} which gives more performance over retrieving metadata data. The metadata is cached with In-Memory database to fast access as mentioned in \cref{subse:redis}.
The system generate a unique identifier for each timeseries, and throw out the \acrshort{wdias}, other microservice use it to handle data for fast access.

@@

\emph{Timeseries} endpoints allow to interact with Metadata Adapter, and those are cache on the Query Handler in order to perform search queries. These are the main endpoints to handle timeseries metadata which defines unique timeseries identifier based on the metadata values. As an example, if it needs to extend the system to store irregular grid data, then it should add another set of location endpoints for storing irregular grid location details.
\begin{itemize}
    \item parameter
    \begin{itemize}
        \item \texttt{GET /parameter} -- Get parameters
        \item \texttt{POST /parameter} -- Create parameter
        \item \texttt{PUT /parameter/id} -- Update parameter
        \item \texttt{DELETE /parameter/id} -- Delete parameter
    \end{itemize}
    \item timeStep
    \begin{itemize}
        \item \texttt{GET timestep} -- Get TimeSteps
        \item \texttt{POST timestep} -- Create TimeStep
        \item \texttt{PUT timestep/id} -- Update TimeStep
        \item \texttt{DELETE timestep/id} -- Delete TimeStep
    \end{itemize}
\dbc{Format others as above}
    \item location
    \begin{itemize}
        \item \emph{GET /location} - Get location points
        \item \emph{POST /location} - Create location point
        \item \emph{PUT /location/id} - Update location point
        \item \emph{DELETE /location/id} - Delete location point
        \item \emph{GET /location/regular-grid} - Get regular grids
        \item \emph{POST /location/regular-grid} - Create regular grid
        \item \emph{PUT /location/regular-grid/id} - Update regular grid
        \item \emph{DELETE /location/regular-grid/id} - Delete regular grid
    \end{itemize}
    \item timeseries
    \begin{itemize}
        \item \emph{GET /timeseries} - Get timeseries
        \item \emph{POST /timeseries} - Create timeseries
        \item \emph{PUT /timeseries/id} - Update timeseries
        \item \emph{DELETE /timeseries/id} - Delete timeseries
    \end{itemize}
\end{itemize}

\emph{Import} endpoints allow to upload data into the \acrshort{wdias} system.
\begin{itemize}
    \item \texttt{POST import/json/raw} -- Insert Scalar/Vector timeseries data with JSON body
    \item \texttt{POST import/csv/raw} -- Insert Scalar/Vector timeseries data in CSV format
    \item \texttt{POST import/ascii-grid/upload} -- Upload set of ASCII Grid files
    \item \texttt{POST import/ascii-grid/binary} -- Upload a single ASCII Grid file
\end{itemize}

\emph{Export} endpoints allow to get/download data from the \acrshort{wdias} system.
\begin{itemize}
    \item \texttt{GET export/json/raw} -- Get Scalar/Vector timeseries data in JSON format
    \item \texttt{GET export/json/raw?start=2000-01-01\&end=2000-01-03} -- Get Scalar/Vector timeseries data in JSON format for given time period
    \item \texttt{GET export/netcdf/binary} -- Download Grid data timeseries data in \acrshort{netCDF} format
\end{itemize}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\acrshort{wdias} Microservices}
\label{sebse:wdias_microservices}
As seen in Figure of \cref{fi:wdias_micro_on_demand} and \cref{fi:wdias_micro_async} each circle represents a microservice, and those are implemented as containerized applications.
\begin{figure}[htp]
    \centering
    \includegraphics[width=1\textwidth]{method/microservice/microservice_architecture-handle_on_demand-v3.jpg}
    \caption{\acrshort{wdias} architecture for handling requests on demand}
    \label{fi:wdias_micro_on_demand}
\end{figure}
Left side of \cref{fi:wdias_micro_on_demand} shows the import modules of the \acrshort{wdias}, and right side shows the export modules. As it explained section \cref{subse:dumb_pipes}, each import microservice only do specific task of converting and forwarding the request to the correct data adapter module.
For each data type, there is a adapter microservice is running which is optimized to storing such type of data. And the metadata data of the timeseries store using \acrshort{rdbms} which gives more performance over retrieving metadata data. The metadata is cached with In-Memory database to fast access as mentioned in \cref{subse:redis}.
The system generate a unique identifier for each timeseries, and through out the \acrshort{wdias}, other microservice use it to handle data for fast access.

@@

\emph{Timeseries} endpoints allow to interact with Metadata Adapter, and those are cache on the Query Handler in order to perform search queries. These are the main endpoints to handle timeseries metadata which defines unique timeseries identifier based on the metadata values. As an example, if it needs to extend the system to store irregular grid data, then it should add another set of location endpoints for storing irregular grid location details.
\begin{itemize}
    \item parameter
    \begin{itemize}
        \item \texttt{GET /parameter} -- Get parameters
        \item \texttt{POST /parameter} -- Create parameter
        \item \texttt{PUT /parameter/id} -- Update parameter
        \item \texttt{DELETE /parameter/id} -- Delete parameter
    \end{itemize}
    \item timeStep
    \begin{itemize}
        \item \texttt{GET /timestep} -- Get TimeSteps
        \item \texttt{POST /timestep} -- Create TimeStep
        \item \texttt{PUT /timestep/id} -- Update TimeStep
        \item \texttt{DELETE /timestep/id} -- Delete TimeStep
    \end{itemize}
\dbc{Format others as above}
    \item location
    \begin{itemize}
        \item \texttt{GET /location} -- Get location points
        \item \texttt{POST /location} -- Create location point
        \item \texttt{PUT /location/id} -- Update location point
        \item \texttt{DELETE /location/id} -- Delete location point
        \item \texttt{GET /location/regular-grid} -- Get regular grids
        \item \texttt{POST /location/regular-grid} -- Create regular grid
        \item \texttt{PUT /location/regular-grid/id} -- Update regular grid
        \item \texttt{DELETE /location/regular-grid/id} -- Delete regular grid
    \end{itemize}
    \item timeseries
    \begin{itemize}
        \item \texttt{GET /timeseries} -- Get timeseries
        \item \texttt{POST /timeseries} -- Create timeseries
        \item \texttt{PUT /timeseries/id} -- Update timeseries
        \item \texttt{DELETE /timeseries/id} -- Delete timeseries
    \end{itemize}
\end{itemize}

\emph{Import} endpoints allow to upload data into the \acrshort{wdias} system.
\begin{itemize}
    \item \texttt{POST /import/json/raw} -- Insert Scalar/Vector timeseries data with JSON body
    \item \texttt{POST /import/csv/raw} -- Insert Scalar/Vector timeseries data in CSV format
    \item \texttt{POST /import/ascii-grid/upload} -- Upload set of ASCII Grid files
    \item \texttt{POST /import/ascii-grid/binary} -- Upload a single ASCII Grid file
\end{itemize}

\emph{Export} endpoints allow to get/download data from the \acrshort{wdias} system.
\begin{itemize}
    \item \texttt{GET /export/json/raw} -- Get Scalar/Vector timeseries data in JSON format
    \item \texttt{GET /export/json/raw?start=2000-01-01\&end=2000-01-03} -- Get Scalar/Vector timeseries data in JSON format for given time period
    \item \texttt{GET /export/netcdf/binary} -- Download Grid data timeseries data in \acrshort{netCDF} format
\end{itemize}

### 2020-02-14 results/sec_3-observations.tex
change API with texttt

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_15m_res_latencies_against_hits.png}
    \caption{Load testing with 15 minutes data - Latency against server hits}
    \label{fi:test_obs_all_15m_latency}
\end{figure}
\ref{fi:test_obs_all_15m_latency} graph provides a overview of the variation of latency over elapsed time of the test plan against number of server hits per second for 15min data.
This graph show that over the time \acrshort{wdias} were able to keep the latency constant over the test plan. But at the peak time, it tend to vary from the mean value a lot.
One noticeable fact is, throw out the test time period, it shows spikes in latency when compared to \ref{fi:test_obs_all_60m_latency} and \cref{fi:test_obs_all_30m_latency}.

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all_auto/obs_all_auto_15m_transaction_throughtput_vs_threads.png}
    \caption{Load testing with 15 minutes data with enabled auto scaling - Latency against server hits}
    \label{fi:test_obs_all_auto_15m_latency}
\end{figure}
\ref{fi:test_obs_all_auto_15m_latency} graph provides an overview of the variation of latency over elapsed time of the test plan against number of server hits per second for 15min data while auto scaling enabled for \acrshort{k8s}.
This graph show that over the time \acrshort{wdias} were able to keep the latency constant over the test plan.
When compared to \ref{fi:test_obs_all_15m_latency}, throw out the test time period, the latency spikes become less.

>>>>

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_15m_res_latencies_against_hits.png}
    \caption{Load testing with 15 minutes data - Latency against server hits}
    \label{fi:test_obs_all_15m_latency}
\end{figure}
\ref{fi:test_obs_all_15m_latency} graph provides a overview of the variation of latency over elapsed time of the test plan against number of server hits per second for 15min data.
This graph show that over the time \acrshort{wdias} were able to keep the latency constant over the test plan. But at the peak time, it tend to vary from the mean value a lot.
One noticeable fact is, through out the test time period, it shows spikes in latency when compared to \ref{fi:test_obs_all_60m_latency} and \cref{fi:test_obs_all_30m_latency}.

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all_auto/obs_all_auto_15m_transaction_throughtput_vs_threads.png}
    \caption{Load testing with 15 minutes data with enabled auto scaling - Latency against server hits}
    \label{fi:test_obs_all_auto_15m_latency}
\end{figure}
\ref{fi:test_obs_all_auto_15m_latency} graph provides an overview of the variation of latency over elapsed time of the test plan against number of server hits per second for 15min data while auto scaling enabled for \acrshort{k8s}.
This graph show that over the time \acrshort{wdias} were able to keep the latency constant over the test plan.
When compared to \ref{fi:test_obs_all_15m_latency}, through out the test time period, the latency spikes become less.
